\documentclass[titlepage]{article}
\usepackage[left=15mm,right=15mm,top=1in,bottom=1in]{geometry}
\begin{document}
\title{Stone Identification App \\
	Software Requirements Specification}
\author{Genevieve Okon (Okong), Sydney Lieng(),\\
	Niko Savas(), Nick Lago(lagond),\\
	Eric Le Fort(leforte)}
\date{\today}
\maketitle

%NOTES:
% Highlight terms that are defined in Section 1.3 (Definitions, Acronyms, and Abbreviations) with bold, italic or underline
% Uniquely number each of your requirements for easy identification and cross-referencing

\section{Non-Functional Requirements}
\subsection{Look \& Feel Requirements}
\subsubsection{Appearance Requirements}
\subsubsection{Style Requirements}

\subsection{Usability \& Humanity Requirements}
\subsubsection{Ease of Use Requirements}
\subsubsection{Personalization \& Internalization Requirements}
\subsubsection{Learning Requirements}
\subsubsection{Understandability \& Politeness Requirements}
\subsubsection{Accessibility Requirements}

\subsection{Performance Requirements}
\subsubsection{Speed \& Latency Requirements}
\subsubsection{Safety Critical Requirements}
\subsubsection{Precision \& Accuracy Requirements}
\subsubsection{Reliability and Availability Requirements}
\textbf{RA1:}This system is available on the user's machine and does not rely on other factors to function. This program should be available 100\% of the time.
\subsubsection{Robustness or Fault-Tolerance Requirements}
\textbf{RFT1:} The program shall be designed in a way that faulty inputs are not possible to select.
\textbf{RFT2:} The program shall return the correct identification for a rock at least 80\% of the time.
\subsubsection{Capacity Requirements}
\textbf{CR1:} This program is designed to work independently on a single piece of hardware. If the program operates as stated in the other requirements on the device, this requirement will be satisfied.
\subsubsection{Scalability or Extensibility Requirements}
\subsubsection{Longevity Requirements}

\subsection{Operational \& Environmental Requirements}
\subsubsection{Expected Physical Environment}
\subsubsection{Requirements for Interfacing with Adjacent Systems}
\subsubsection{Productization Requirements}
\subsubsection{Release Requirements}

\subsection{Maintainability \& Support Requirements}
\subsubsection{Maintenance Requirements}
\subsubsection{Supportability Requirements}
\subsubsection{Adaptability Requirements}

\subsection{Security Requirements}
\subsubsection{Access Requirements}
\subsubsection{Integrity Requirements}
\subsubsection{Privacy Requirements}
\subsubsection{Audit Requirements}
\subsubsection{Immunity Requirements}

\subsection{Cultural \& Political Requirements}
\subsubsection{Cultural Requirements}
\textbf{CP1:} This program shall not include any symbols, statements or anything of that nature that may be found offensive to anyone's culture.
\subsubsection{Political Requirements}
\textbf{CP2:} This program shall not include any symbols, statements or anything of that nature that display any sort of political stance.

\subsection{Legal Requirements}
\subsubsection{Compliance Requirements}
\subsubsection{Standards Requirements}


\end{document}