\documentclass[titlepage]{article}
\usepackage[left=15mm,right=15mm,top=1in,bottom=1in]{geometry}
\begin{document}
\title{Stone Identification App \\
	Software Requirements Specification}
\author{Genevieve Okon (Okong), Sydney Lieng(),\\
	Niko Savas(), Nick Lago(lagond),\\
	Eric Le Fort(leforte)}
\date{\today}
\maketitle

\section{Functional Requirements}
\subsection {Business Event: User wants to identify a rock}
	\subsubsection {Viewpoint: Everyday User}
		\begin{itemize}
			\item The application will allow the user to input information about texture, colour, or size of a rock.
			\item The application will estimate the type of rock based on user-inputted texture, colour, and/or size.
			\item The application will suggest rocks based on the user's location.
		\end{itemize}
	\subsubsection {Viewpoint: Developer}
	\subsubsection {Viewpoint: Security Expert}
\subsection {Business Event: User wants to update the database}
	\subsubsection {Viewpoint: Everyday User}
		\begin{itemize}
			\item The every day user will not be able to modify the database.
		\end{itemize}
	\subsubsection {Viewpoint: Developer}
		\begin{itemize}
			\item The developer will be able to update the database with new information
		\end{itemize}
	\subsubsection {Viewpoint: Security Expert}
		\begin{itemize}
			\item The security expert must be able to manage developer access to the database
		\end{itemize}

\subsection{Application identifies cost per weight }
\subsubsection{Application}
\begin{itemize}

  \item The application shall show the cost of the rock according to the weight of the rock. 
  \item The application shall show the cost per gram of the rock.
  \end{itemize}
  \subsubsection{Everyday user}
  \begin{itemize}
  \item The user shall be able to enter the weight of the rock found in the application.
  \item The users shall be provided with possible places to sell rocks found.
  
\end{itemize}

\subsection{Application displays image}
\subsubsection{Application}
\begin{itemize}
\item The application shall display images of possible matches for rocks according to user input.
\end{itemize}
  \subsubsection{Everyday user}
  \begin{itemize}
  \item The user shall be able to view the image of final rock match found.
\end{itemize}


\subsection{User searches for rock name}
\subsubsection{Application}
\begin{itemize}

  \item The application shall search for rock name according to the categories the user chooses.
  \item The application shall eliminate non possible rocks as the user specifies more about rock found. 
  \item The application shall be able to access the database to find possible rock information. 
  \end{itemize}
    \subsubsection{Everyday user}
  \begin{itemize}
  \item The user shall be able to view name, location and properties of rock match found. 
\end{itemize}

\end{document}