\documentclass[titlepage]{article}
\usepackage[left=15mm,right=15mm,top=1in,bottom=1in]{geometry}
\usepackage{graphicx}

\title{Stone Identification App \\
Software Requirements Specification}
\author{Genevieve Okon(okong), Sydney Lieng(liengsn),\\
Niko Savas(savasn), Nick Lago(lagond),\\
Eric Le Fort(leforte)}
\date{\today}

\begin{document}
\maketitle
\newpage

\section{Introduction}~\\
This document will explain the design of the Stone Identification App using, Use Case Diagram, Analysis Class Diagram, Architectural Design and Class Responsibility Collaboration Cards. 

\subsection{Purpose}{
The purpose of this document is to describe the design architecture of the Stone Identification App. This will be achieved through a series of different diagrams and analysis techniques. The indented audience for this document is the software implementation team as well as the client.
}

\subsection{System Description}{
The system that will be discussed in this report is that of the Stone Identification App. The system will be composed of multiple expert classes. Each of these classes will have access to a database containing a list of rocks and the details pertaining to those rocks. When a customer inputs information about a rock the system will use these experts to give a list of possible rocks they may have found. The user will be able to keep information on rocks they have found on a separate database held on local storage devices. The system will be designed as an android application. It will be able to be used on any android devices and will be purchased through the android app store. 
}

\subsection{Overview}{
This document has 4 sections not including this one. Each sections contains either a design diagram or an explanation that will further describe the design architecture of the Stone Identification App. Each section will provide insight into a key aspect of design with the goal of preparing the software team for implementation.
\begin{itemize}
\item \textbf{Use Case:} This document will show who interacts with the system as well as the intended results of those interactions through Use Case Diagrams
\item \textbf{Analysis Class Diagram:} The Analysis Class Diagram will outline which classes will be a boundary, controller or entity class and show their connections to one another
\item \textbf{Architectural Design Class:} This section will show the overview of the overall design, and justification for the choice of this design
\item \textbf{Class Responsibility Collaboration Cards} The use of these cards will show what the classes that make up the Stone Identification App key responsibilities are and what other classes they interact with
\end{itemize}
}

\end{document}
